Carbonate chemistry at Ny-Ålesund

### 2021-02-17 awipev-CO2.Rmd
Preparing to calculate monthly availability.

s1 <- summary(as.factor(d_min$pco2_corr_qf))*100/length(d_min$pco2_corr_qf)
s2 <- summary(as.factor(d_min$sal_fb_qf))*100/length(d_min$sal_fb_qf)
s3 <- summary(as.factor(d_min$sal_insitu_ctd_qf))*100/length(d_min$sal_insitu_ctd_qf)
s4 <- summary(as.factor(d_min$temp_fb_qf))*100/length(d_min$temp_fb_qf)
s5 <- summary(as.factor(d_min$temp_insitu_11m_qf))*100/length(d_min$temp_insitu_11m_qf)
# durafet and seafet started later
x <- filter(d_min, datetime >= as.POSIXct("2017-08-29 10:00:00"))
#s6 <- summary(as.factor(x$temp_dur_qf))*100/length(x$temp_dur_qf)
s7 <- summary(as.factor(x$ph_dur_qf))*100/length(x$ph_dur_qf)
x <- filter(d_min, datetime >= as.POSIXct("2017-08-24 19:00:00"))
s8 <- summary(as.factor(x$phINT_qf))*100/length(x$phINT_qf)
z <- t(bind_rows(s1,s2,s3,s4,s5,s7,s8)) %>%
  as.data.frame() %>%
         rownames_to_column(var = "flag") %>% 
         as_tibble()
labels <- c("Good", "Not usable", "Outside regional range", "Outliers (despike)", 
            "Failed visual inspection", "Not deployed or operated", "Acid flush", "Failed visual inspection")
colnames(z) <- c("Flag", "pCO2", "Salinity FerryBox", "In situ salinity", 
                 "Temperature FerryBox", "In situ temperature", "Durafet pH", "seaFET pH")
zz <- pivot_longer(z, -Flag)
p <- ggplot(data = zz, aes(x = name, y = value, fill = Flag)) +
  geom_bar(position = position_stack(reverse = TRUE), stat="identity", width = 0.3) +
  #scale_y_reverse() +
  scale_fill_discrete(labels = labels) + 
  coord_flip() +
  #geom_text(aes(label=round(value, digits = 0)), position = position_stack((hjust = 0.5)), size = 3) +
  labs(x="", y="", title = "Distribution (%) of quality flags", color = "Quality flag") +
  Mytheme(size_labs = 8) +
  theme(plot.margin = margin(t = 0, r = 0.0, b = 0, l = 0.0, unit = "cm"))
ggsave(filename = "figures/availability.png", plot = p, width = 20, units = "cm")
kable(z, digits = 1)
rm(d_min)
```

>>>>

s1 <- summary(as.factor(d_min$pco2_corr_qf))*100/length(d_min$pco2_corr_qf)
s2 <- summary(as.factor(d_min$sal_fb_qf))*100/length(d_min$sal_fb_qf)
s3 <- summary(as.factor(d_min$sal_insitu_ctd_qf))*100/length(d_min$sal_insitu_ctd_qf)
s4 <- summary(as.factor(d_min$temp_fb_qf))*100/length(d_min$temp_fb_qf)
s5 <- summary(as.factor(d_min$temp_insitu_11m_qf))*100/length(d_min$temp_insitu_11m_qf)
# durafet and seafet started later
x <- filter(d_min, datetime >= as.POSIXct("2017-08-29 10:00:00"))
#s6 <- summary(as.factor(x$temp_dur_qf))*100/length(x$temp_dur_qf)
s7 <- summary(as.factor(x$ph_dur_qf))*100/length(x$ph_dur_qf)
x <- filter(d_min, datetime >= as.POSIXct("2017-08-24 19:00:00"))
s8 <- summary(as.factor(x$phINT_qf))*100/length(x$phINT_qf)
z <- t(bind_rows(s1,s2,s3,s4,s5,s7,s8)) %>%
  as.data.frame() %>%
         rownames_to_column(var = "flag") %>% 
         as_tibble()
labels <- c("Good", "Not usable", "Outside regional range", "Outliers (despike)", 
            "Failed visual inspection", "Not deployed or operated", "Acid flush", "Failed visual inspection")
colnames(z) <- c("Flag", "pCO2", "Salinity FerryBox", "In situ salinity", 
                 "Temperature FerryBox", "In situ temperature", "Durafet pH", "seaFET pH")
zz <- pivot_longer(z, -Flag)
p <- ggplot(data = zz, aes(x = name, y = value, fill = Flag)) +
  geom_bar(position = position_stack(reverse = TRUE), stat="identity", width = 0.3) +
  #scale_y_reverse() +
  scale_fill_discrete(labels = labels) + 
  coord_flip() +
  #geom_text(aes(label=round(value, digits = 0)), position = position_stack((hjust = 0.5)), size = 3) +
  labs(x="", y="", title = "Distribution (%) of quality flags", color = "Quality flag") +
  Mytheme(size_labs = 8) +
  theme(plot.margin = margin(t = 0, r = 0.0, b = 0, l = 0.0, unit = "cm"))
ggsave(filename = "figures/availability.png", plot = p, width = 20, units = "cm")
kable(z, digits = 1)

# Good data per year

rm(d_min)
```
